MLH1 Results Outline

### 2020-01-30 doc/Main_Report_Results.rmd
organizing Mixed Model results

Details of data set cleaning ect is in SetupData.rmd
Effects from different factors are reviewed in Effects.Rmd

@@

table(DF.HetC.MixedModel$strain, DF.HetC.MixedModel$sex)

@@

table(DF.HetC.MixedModel.HQ$strain, DF.HetC.MixedModel.HQ$sex)

@@

This is the size of mice used within the Mixed model

@@

Can I indedate the average number of cells with go into each mouse.?

FOR FINAL ANALYSIS, make sure that MOL is coded as a separate subsp (change all of the main model reports to). For mouse averages of MLH1 counts, only strain with observations for both sexes and are from Mus species.

@@

@@

@@

ranef(HetC.MixedModel.HQ)
#which is the test for random effects ?!

@@

Above is the table of coefficients for MM.1.mol, molssinus coded as separate subspecies, lme(), random effects strain and strain specific sex effect.

@@

as.data.frame(round(summary(Reduced.strain.HQ)$tTable, 6))
#add a aption to this code chunk
#ranef(Reduced.strain.HQ)

@@

> MM3

@@

> MM.4

@@

references for phenotypic variance connected to robustness to environment, increase in developmental consistancy
Waddington 1942, Rutherford and Lindquist 2998, Mackay and Lyman 2005, Levy and Siegal 2008)

@@

meiotic Checkpoints for ensuring consistancy (Hochwagen and Amon 2006, Li and Schimenti 2007, Jaramillo-Lambert 2010 and Kauppi 2013)

@@

make a smaller propoertion chrm block --

@@

insert male total sc results here

>>>>

Details of data set cleaning etc is in SetupData.rmd
Effects from different factors are reviewed in Effects.Rmd

@@

#table(DF.HetC.MixedModel$strain, DF.HetC.MixedModel$sex)

@@

#table(DF.HetC.MixedModel.HQ$strain, DF.HetC.MixedModel.HQ$sex)

@@

This is the break down of mice used within the Mixed model

@@

<!--Can I indicate the average number of cells with go into each mouse.? -->

@@

*mouse averages exclude Q5 and male counts are adjusted +1 for PAR)*

@@

For now I will focus on 4 different models run mouse averages on MLH1 counts.

1. $$mouse .mean CO ~=~ subsp * sex  + rand(strain*sex) + \varepsilon$$

2. $$mouse .mean CO ~=~ subsp * sex  + rand(1|strain) + \varepsilon$$

3. $$mouse .mean CO ~=~ subsp * sex * strain + \varepsilon$$

4. $$mouse .mean CO ~=~ sex * strain + \varepsilon$$

> Model 1

@@

#ranef(HetC.MixedModel.HQ)
#which is the test for random effects ?!
```

@@

> Model 2.

@@

as.data.frame(round(summary(Reduced.strain.HQ)$tTable, 6))
#add a aption to this code chunk
#ranef(Reduced.strain.HQ)
```

@@

> Model 3

@@

> Model 4

@@

references for phenotypic variance connected to robustness to environment, increase in developmental consistency
Waddington 1942, Rutherford and Lindquist 2998, Mackay and Lyman 2005, Levy and Siegal 2008)

@@

meiotic Checkpoints for ensuring consistency (Hochwagen and Amon 2006, Li and Schimenti 2007, Jaramillo-Lambert 2010 and Kauppi 2013)

@@

make a smaller proportion chrm block --

@@

insert male total SC results here
